Calendar-based graphics for visualizing people's daily schedules

### 2019-05-15 main.Rmd
Spelling errors

abstract: |
  Calendars are broadly used in society to display temporal information and events. This paper describes a new calendar display for plotting data, that includes a layout algorithm with many options, and faceting functionality. The functions use modulus algebra on the date variable to restructure the data into a calendar format. The user can apply the grammar of graphics to create plots inside each calendar cell, and thus the displays synchronize neatly with **ggplot2** graphics. The motivating application is studying pedestrian behavior in Melbourne, Australia, based on counts which are captured at hourly intervals by sensors scattered around the city. Faceting by the usual features such as day and month, was insufficient to examine the behavior. Making displays on a monthly calendar format helps to understand pedestrian patterns relative to events such as work days, weekends, holidays, and special events. The functions for the calendar algorithm are available in the R package **sugrrants**.

@@

```{r boxplot, fig.height = 8, fig.cap = "Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased varibility is noted on the last day of December as approaching towards New Year's Eve.", fig.show = "hide"}
```

@@

```{r dow, fig.height = 7, fig.cap = "Boxplots of daily energy usage against day of week for four households. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability."}
```

@@

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays faceted by each household based on common scales. We can precisely tell each indidual's vacation days and the overnight use for household 2 in mid January."}
```

>>>>

abstract: |
  Calendars are broadly used in society to display temporal information and events. This paper describes a new calendar display for plotting data, that includes a layout algorithm with many options, and faceting functionality. The functions use modulus algebra on the date variable to restructure the data into a calendar format. The user can apply the grammar of graphics to create plots inside each calendar cell, and thus the displays synchronize neatly with **ggplot2** graphics. The motivating application is studying pedestrian behavior in Melbourne, Australia, based on counts which are captured at hourly intervals by sensors scattered around the city. Faceting by the usual features such as day and month, is insufficient to examine the behavior. Making displays on a monthly calendar format helps to understand pedestrian patterns relative to events such as work days, weekends, holidays, and special events. The functions for the calendar algorithm are available in the R package **sugrrants**.

@@

```{r boxplot, fig.height = 8, fig.cap = "Side-by-side boxplots of hourly counts for all the 43 sensors in December 2016, with the loess smooth line superimposed on each day. It shows the hourly distribution in the city as a whole. The increased variability is noted on the last day of December as approaching towards New Year's Eve.", fig.show = "hide"}
```

@@

```{r dow, fig.height = 7, fig.cap = "Boxplots of daily energy usage against day of week for four households. Suggested by the medians, household 3 uses more energy than the others on the week days, due to a large family size. By constrast, household 2 sees considerably larger variability."}
```

@@

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays faceted by each household based on common scales. We can precisely tell each individual's vacation days and the overnight use for household 2 in mid January."}
```
